---
title: "Collatz Conjecture"
author: "Luzi"
date: "6.10.2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

## Collatz Conjecture

Given any integer number $n$, by iterating the following algorithm

1. if it is even, the next number is one half the previous number
2. if it is odd, the next number is three times the previous number plus one

the sequence will always reach one.

**Task:** given any integer number $n$, write a function that implements the Collatz algorithm. Then, write a loop to retrieve the entire sequence. Plot the sequence. 

## Implementing the Collatz algorithm


```{r collatz algorithm}
n <- 33

collatz <- function(n) {
  if (n%%2 == 0) { # is n even?
    n / 2 
  } else {
    (3 * n) + 1
  }
}
```


## Loop: Retrieving the entire sequence
```{r loop}
result <- c()

while (n != 1) {
  n <- collatz(n)
  result <- c(result, n)
}
result
```

## Plotting the sequence


```{r plot}
# result as a tibble
x_axis <- 1:length(result)
plot_data <- tibble(x_axis, result)

ggplot(plot_data, aes(x = x_axis, y = result)) +
  geom_line() +
  geom_point(color = "tomato") +
  labs(x = "", y = "Collatz Result")
```

